---
title: "Hands-on_Ex09"
author: Yebin Du
---

# Modelling, Visualising and Analysing Network Data with R

## Getting Started
```{r}
pacman::p_load(igraph, tidygraph, ggraph, 
               visNetwork, lubridate, clock,
               tidyverse, graphlayouts)
```


```{r}
GAStech_nodes <- read_csv("data/GAStech_email_node.csv",show_col_types = FALSE)
GAStech_edges <- read_csv("data/GAStech_email_edge-v2.csv",show_col_types = FALSE)
```



## Reviewing the imported data
```{r}
library(dplyr)  # To install only dplyr

glimpse(GAStech_edges)
```



## Data Wrangling
```{r}
library(lubridate)
GAStech_edges <- GAStech_edges %>%
  mutate(SendDate = dmy(SentDate)) %>%
  mutate(Weekday = wday(SentDate,
                        label = TRUE,
                        abbr = FALSE))
```


## Wrangling attributes
```{r}
GAStech_edges_aggregated <- GAStech_edges %>%
  filter(MainSubject == "Work related") %>%
  group_by(source, target, Weekday) %>%
  summarise(Weight = n(), .groups = "drop") %>%
  filter(source!=target) %>%
  filter(Weight > 1)
```



## Using tbl_graph() to build tidygraph data model.
```{r}
library(tidygraph)

GAStech_graph <- tbl_graph(nodes = GAStech_nodes,
                           edges = GAStech_edges_aggregated, 
                           directed = TRUE)
```


## Reviewing the output tidygraph’s graph object
```{r}
GAStech_graph
```



## Changing the active object
```{r}
GAStech_graph %>%
  activate(edges) %>%
  arrange(desc(Weight))
```



## Plotting a basic network graph
```{r}
library(ggraph)

ggraph(GAStech_graph) +
  geom_edge_link() +
  geom_node_point()
```



## Changing the default network graph theme
```{r}
g <- ggraph(GAStech_graph) + 
  geom_edge_link(aes()) +
  geom_node_point(aes())

g + theme_graph()
```



## Changing the coloring of the plot
```{r}
g <- ggraph(GAStech_graph) + 
  geom_edge_link(aes(colour = 'grey50')) +
  geom_node_point(aes(colour = 'grey40'))

g + theme_graph(background = 'grey10',
                text_colour = 'white')
```



## Fruchterman and Reingold layout 
```{r}
g <- ggraph(GAStech_graph, 
            layout = "fr") +
  geom_edge_link(aes()) +
  geom_node_point(aes())

g + theme_graph()
```



## Modifying network nodes
```{r}
g <- ggraph(GAStech_graph, 
            layout = "nicely") + 
  geom_edge_link(aes()) +
  geom_node_point(aes(colour = Department, 
                      size = 3))

g + theme_graph()
```



## Modifying edges
```{r}
g <- ggraph(GAStech_graph, 
            layout = "nicely") +
  geom_edge_link(aes(width=Weight), 
                 alpha=0.2) +
  scale_edge_width(range = c(0.1, 5)) +
  geom_node_point(aes(colour = Department), 
                  size = 3)

g + theme_graph()
```


## Creating facet graphs

### Working with facet_edges()
```{r}
set_graph_style()

g <- ggraph(GAStech_graph, 
            layout = "nicely") + 
  geom_edge_link(aes(width=Weight), 
                 alpha=0.2) +
  scale_edge_width(range = c(0.1, 5)) +
  geom_node_point(aes(colour = Department), 
                  size = 2)

g + facet_edges(~Weekday)
```



### Working with facet_edges()
```{r}
set_graph_style()

g <- ggraph(GAStech_graph, 
            layout = "nicely") + 
  geom_edge_link(aes(width=Weight), 
                 alpha=0.2) +
  scale_edge_width(range = c(0.1, 5)) +
  geom_node_point(aes(colour = Department), 
                  size = 2) +
  theme(legend.position = 'bottom')
  
g + facet_edges(~Weekday)
```



### A framed facet graph
```{r}
set_graph_style() 

g <- ggraph(GAStech_graph, 
            layout = "nicely") + 
  geom_edge_link(aes(width=Weight), 
                 alpha=0.2) +
  scale_edge_width(range = c(0.1, 5)) +
  geom_node_point(aes(colour = Department), 
                  size = 2)
  
g + facet_edges(~Weekday) +
  th_foreground(foreground = "grey80",  
                border = TRUE) +
  theme(legend.position = 'bottom')
```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```



### 
```{r}

```


